Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-09 acl.2016/acl2016.tex
bool -> size_t. Prevent segfault when using mempool

However, the model's query keys are the source and target phrase of each translation rule. Rather than storing the lexicalized re-ordering model separately, we shall integrating it into the translation model, eliminating the need to query a separate file. This has precedent in ~\newcite{peitz2012jane} but the effect on decoding speed were not published. We will compare results with using a separate model in this paper.

@@

As a baseline, we use a recent\footnote{between January and June 2016} version of the Moses decoder taken from the github repository.

>>>>

However, the model's query keys are the source and target phrase of each translation rule. Rather than storing the lexicalized re-ordering model separately, we shall integrating it into the translation model, eliminating the need to query a separate file. The lexicalized reordering model retains its own weights in the log-linear framework. The total weighted score is expected to be identical to the Moses baseline apart from rare training configurations where the lexicalized reordering model is trained on a different dataset than the translation model.

This optimization has precedent in ~\newcite{peitz2012jane} but the effect on decoding speed were not published. We will compare results with using a separate model in this paper.

@@

As a baseline, we use a recent\footnote{as at 8th June, 2016, commit hash 482457bf2bbb5673fbab5f663da5fd3d78ed132f } version of the Moses decoder taken from the github repository.
